
For this code to work, your current working directory you should have the following:

- this rmd file
- a folder called "results" with in it, a csv file called "master_dataset.csv" (this is obtained by running the ipynb notebook)

After running this rmd file once, within the already existing "results" folder, a new folder will appear named "statistical_analysis". Here, you will find the following:
- **accuracy_regression txt file and png file**: the results and a plot of the multiple linear regression model that predicts model accuracy from model size and political persona 
- **bias_regression txt file and png file**: the results and a plot of the multiple linear regression model that predicts model bias from model size and political persona 


```{r}

# install packages

install.packages("readr")

library(readr)
library(stringr)
library(dplyr)
library(ggplot2)

```


```{r}
# preprocessing of dataframe

df <- read_csv("results/master_dataset.csv")

df$model_size_num <- str_extract(
  df$model_size,
  "\\d+\\.?\\d*"
)

df$model_size_num <- as.numeric(
  df$model_size_num
)

df$persona <- as.factor(df$persona)


# set results relative to their baseline model

agg_df <- df %>%
  group_by(model_size_num, persona) %>%
  summarise(
    accuracy = mean(correct, na.rm = TRUE),
    bias_score = mean(bias_score, na.rm = TRUE)
  )
agg_df$persona <- relevel(agg_df$persona, ref = "Baseline")

```


```{r}
# accuracy linear correlation

accuracy_model <- lm(
  accuracy ~ log(model_size_num) * persona,
  data = agg_df
)

summary(accuracy_model)
anova(accuracy_model)

# plot
ggplot(
  agg_df,
  aes(
    x = model_size_num,
    y = accuracy,
    color = persona
  )
) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_log10()

```


```{r}
# bias score linear correlation

bias_model <- lm(
  bias_score ~ log(model_size_num) * persona,
  data = agg_df
)

summary(bias_model)
anova(bias_model)


# plot 
ggplot(
  agg_df,
  aes(
    x = model_size_num,
    y = bias_score,
    color = persona
  )
) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_log10()

```


```{r}

# save as image files

# create results folder if it does not exist
if (!dir.exists("results")) {
  dir.create("results")
}

# create statistical analysis folder
if (!dir.exists("results/statistical_analysis")) {
  dir.create("results/statistical_analysis")
}

accuracy_plot <- ggplot(
  agg_df,
  aes(
    x = model_size_num,
    y = accuracy,
    color = persona
  )
) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_log10() +
  ggtitle("Accuracy vs Model Size")

ggsave(
  filename = "results/statistical_analysis/accuracy_regression.png",
  plot = accuracy_plot,
  width = 10,
  height = 6,
  dpi = 300
)


bias_plot <- ggplot(
  agg_df,
  aes(
    x = model_size_num,
    y = bias_score,
    color = persona
  )
) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_log10() +
  ggtitle("Bias Score vs Model Size")

ggsave(
  filename = "results/statistical_analysis/bias_regression.png",
  plot = bias_plot,
  width = 10,
  height = 6,
  dpi = 300
)


capture.output(
  summary(accuracy_model),
  file = "results/statistical_analysis/accuracy_model_summary.txt"
)

capture.output(
  summary(bias_model),
  file = "results/statistical_analysis/bias_model_summary.txt"
)

```


